---
title: "Ex_Logistic_Regression"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Exercises
Using the spam data set from the kernlab package:
```{r}
library(tidyverse)
library(kernlab) # to import data set
# Helper packages
library(dplyr)     # for data wrangling
library(ggplot2)   # for awesome plotting
library(rsample)   # for data splitting

# Modeling packages
library(caret)     # for logistic regression modeling

# Model interpretability packages
library(vip)       # variable importance
library(ROCR)  

```
Import and Split data also change response variable type 
```{r}
data(spam)
dfspam <- spam 

#change response variable to binary
dfspam$type <- ifelse(dfspam$type == "spam", 1, 0)
str(dfspam)
# change categorical variables to factors
dfspam$type = as.factor(dfspam$type)

str(spam)
set.seed(123)
spam_split <- initial_split(dfspam, prop = .7, strata = "type")
spam_train <- training(spam_split)
spam_test  <- testing(spam_split)
```
Drop NA if there is any 
```{r}
dfspam <- drop_na(dfspam)
```

```{r}
# make sure type has convert correctly
head(spam_train$type)

```

Explor data 
```{r}
head(dfspam)
describe(dfspam)
```
## Ex.1_Pick a single feature and apply simple logistic regression model.

### model 1st feature [report]
```{r}
# fit model to 1st feature report
model1 <- glm(type ~ report, family = "binomial", data = spam_train)
tidy(model1)
```
### Ex.1.1_Interpret the feature’s coefficient
```{r}
exp(coef(model1))
```
### Ex.1.2_What is the model’s performance?

What metric do we look at? At this point you haven't predicted anything, so it's hard to say. Normally, you'd take the accuracy, the confusion matrix or the ROC after fitting the model with (predict())



## Ex.2_Pick another feature to add to the model.

### Ex.2.1_Before applying the module why do you think this feature will help?
I'm curious to see if the message was reported and message have num415 can this give a pattern to predict if the message is spam?

## Ex.2.2_Apply a logistic regression model with the two features and compare to the simple linear model.
### model 2 feature [report & num415]
```{r}
model2 <- glm(type ~ report + num415, family = "binomial", data = spam_train)
tidy(model2)
```
### Ex.2.3_Interpret the coefficients.
```{r}
exp(coef(model2))
```

## Ex.3_Now apply a model that includes all the predictors.
# model all features 
```{r}
model3 <- glm(type ~ report + num415, family = "binomial", data = spam_train)
tidy(model3)
```
Interpret the coefficients for model 3.
```{r}
exp(coef(model3))
```
## Ex.3.1_How does this model compare to the previous two?


```{r}
# Assessing models accuracy
set.seed(123)
cv_model1 <- train(
  type ~ report, 
  data = spam_train, 
  method = "glm",
  family = "binomial",
  trControl = trainControl(method = "cv", number = 10)
)
set.seed(123)
cv_model2 <- train(
  type ~ report + num415, 
  data = spam_train, 
  method = "glm",
  family = "binomial",
  trControl = trainControl(method = "cv", number = 10)
)
set.seed(123)
cv_model3 <- train(
  type ~ . , 
  data = spam_train, 
  method = "glm",
  family = "binomial",
  trControl = trainControl(method = "cv", number = 10)
)
# extract out of sample performance measures
summary(
  resamples(
    list(
      model1 = cv_model1, 
      model2 = cv_model2, 
      model3 = cv_model3
    )
  )
)$statistics$Accuracy
```

## Ex.5_Compute and interpret the following performance metrics:
No information rate
accuracy rate
sensitivity
specificity

(accuracy, confusion matrix, ROC plot)

```{r glm-confusion-matrix_model1}
# Confusion matrix

# predict class
pred_class_model1 <- predict(cv_model1, spam_train)

# create confusion matrix
confusionMatrix(
  data = relevel(pred_class_model1, ref = "1"), 
  reference = relevel(spam_train$type, ref = "1")
)
# 15/(15+1255) = 0.011811 (sensitivity)

# (15 + 1928)/(15 + 1928 + 1255 + 24) = 0.603 # accuracy
```

```{r glm-confusion-matrix}
# Confusion matrix

# predict class
pred_class <- predict(cv_model3, spam_train)

# create confusion matrix
confusionMatrix(
  data = relevel(pred_class, ref = "1"), 
  reference = relevel(spam_train$type, ref = "1")
)
```

## Ex.4_Plot an ROC curve comparing the performance of all three models
```{r}
# Compute predicted probabilities
m1_prob <- predict(cv_model1, spam_train, type = "prob")
m3_prob <- predict(cv_model3, spam_train, type = "prob")

m1_prob <- m1_prob$`1` #short formula^^
m3_prob <- m3_prob$`1` #short formula^^

# Compute AUC metrics for cv_model1 and cv_model3
perf1 <- prediction(m1_prob, spam_train$type) %>%
  performance(measure = "tpr", x.measure = "fpr")

perf2 <- prediction(m3_prob, spam_train$type) %>%
  performance(measure = "tpr", x.measure = "fpr")

# Plot ROC curves for cv_model1 and cv_model3
plot(perf1, col = "black", lty = 2)
plot(perf2, add = TRUE, col = "blue")
legend(0.8, 0.2, legend = c("cv_model1", "cv_model3"),
       col = c("black", "blue"), lty = 2:1, cex = 0.6)
```



