---
title: "Ex_Regularized_Regression"
author: "Ghadi K"
date: "08-11-2020"
output: 
  html_document:
    theme: journal
    highlight: espresso
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=FALSE , warning=FALSE, message=FALSE}
# Helper packages
library(recipes)   # for feature engineering
library(tidyverse) # general data munging
# Modeling packages
library(glmnet)   # for implementing regularized regression
library(caret)    # for automating the tuning process
library(rsample)  # for sampling
# Model interpretability packages
library(vip)      # for variable importance
```
Using the Hitters dataset from the ISLR package I solve the following questions:

```{r}
# import dataset
data(Hitters, package = "ISLR")
head(Hitters)
Hitters <- drop_na(Hitters)
# split data
set.seed(123)
split <- initial_split(Hitters, strata = "Salary")
Hitters_train <- training(split)
```


```{r, echo=FALSE , warning=FALSE, message=FALSE}
# Create training  feature matrices
X <- model.matrix(Salary ~ ., Hitters_train)[, -1]
Y <- log(Hitters_train$Salary)
```
#Question 1
Apply a ridge model with glmnet with Salary being the response variable.
    What is the minimum MSE?
    What is the minimum MSE within 1 standard error?
    What are the lambda values for these MSEs?

```{r, echo=FALSE , warning=FALSE, message=FALSE}
#ridge 
ridge <- glmnet(
  x = X,
  y = Y,
  alpha = 0
)

plot(ridge, xvar = "lambda")

```


```{r, echo=FALSE , warning=FALSE, message=FALSE}
# Ridge CV model
  ridge <- cv.glmnet(
  x = X,
  y = Y,
  alpha = 0
)

plot(ridge)
```


```{r, echo=FALSE , warning=FALSE, message=FALSE}
###Ridge model results
#minimum MSE
min(ridge$cvm)
#lambda for this min MSE
ridge$lambda.min 
ridge$cvm[ridge$lambda == ridge$lambda.1se]
ridge$nzero[ridge$lambda == ridge$lambda.1se]
```

#Question 2
Apply a lasso model with glmnet.
    What is the minimum MSE?
    What is the minimum MSE within 1 standard error?
    What are the lambda values for these MSEs?

```{r, echo=FALSE , warning=FALSE, message=FALSE}

# Lasso
lasso <- glmnet(
  x = X,
  y = Y,
  alpha = 1
)

plot(lasso, xvar = "lambda")

```

```{r, echo=FALSE , warning=FALSE, message=FALSE}

# Lasso CV model
lasso <- cv.glmnet(
  x = X,
  y = Y,
  alpha = 1
)

plot(lasso)
```

```{r, echo=FALSE , warning=FALSE, message=FALSE}
##Lasso model results
#minimum MSE
min(lasso$cvm)       
# lambda for this min MSE
lasso$lambda.min 
lasso$cvm[lasso$lambda == lasso$lambda.1se]
lasso$nzero[lasso$lambda == lasso$lambda.1se]
```
#Question 3
Perform a grid search across alpha parameter values ranging between 0–1.
    What is the optimal alpha and lambda values?
    What is the MSE and RMSE for this optimal model?
    How does it compare to your previous models?
```{r, echo=FALSE , warning=FALSE, message=FALSE}
# Grid search
hyper_grid <- expand.grid(
  alpha = seq(0, 1, by = .25),
  lambda = c(0.1, 10, 100, 1000, 10000)
)

# perform resampling
set.seed(123)
cv_glmnet <- train(
  x = X,
  y = Y,
  method = "glmnet",
  preProc = c("zv", "center", "scale"),
  trControl = trainControl(method = "cv", number = 10),
  tuneLength = 10
)
# best model
cv_glmnet$results %>%
  filter(
    alpha == cv_glmnet$bestTune$alpha,
    lambda == cv_glmnet$bestTune$lambda
  )
# plot results
plot(cv_glmnet)
```

```{r, echo=FALSE , warning=FALSE, message=FALSE}
# Comparing results to previous models
pred <- predict(cv_glmnet, X)
RMSE(exp(pred), exp(Y))
```
#Question 4
Plot the top 10 most influential features. Do these features have positive or negative impacts on your response variable?
Seeing plot result we can say that some features have positive while other have negative impacts
```{r, echo=FALSE , warning=FALSE, message=FALSE}
# Feature importance
vip(cv_glmnet, num_features = 20, geom = "point")
```

